D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-06 ootavacuous.tex
"Non-Trivial Semantic Dependencies": Add initial-value/OOTA footnote
Examining an execution can identify OOTA cycles whose values happen to
match the initial values, even though software could not distinguish them.

Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Because the only two solutions to $x^2 = x$ are the values zero and one,
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Multiplication Example, Initial Value 1}
each have only one OOTA cycle, and an execution having initial values
of (say) two could have at most two OOTA cycles.
Listing~\ref{lst:OOTA Three-Factor Multiplication Example, Initial Value Zero}
goes one step further by multiplying the values obtained from three
different loads.
Because $x^3 = x$ has three solutions ($\left\{ -1, 0, 1 \right\}$),
this execution could have up to three OOTA cycles.

>>>>

Because the only two solutions to $x^2 = x$ are the values zero and one,
Listings~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
and~\ref{lst:OOTA Multiplication Example, Initial Value 1}
each have only one OOTA cycle,\footnote{
	Note well that the initial values cannot be said to have come
	out of thin air.
	Although it is possible to have an OOTA cycle that does not
	involve the initial values, but happens to have the same value,
	the software would not be able to tell the difference.}
and an execution having initial values
of (say) two could have at most two OOTA cycles.
Listing~\ref{lst:OOTA Three-Factor Multiplication Example, Initial Value Zero}
goes one step further by multiplying the values obtained from three
different loads.
Because $x^3 = x$ has three solutions ($\left\{ -1, 0, 1 \right\}$),
this execution could have up to three OOTA cycles.
